---
title: "Bootstrapping"
author: "Nidhi Patel"
date: "12/10/2020"
output: github_document
---
```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Simulate data

```{r}
n_samp = 250

sim_df_const = tibble(
  x = rnorm(n_samp, 1, 1),
  error = rnorm(n_samp, 0, 1),
  y = 2 + 3 * x + error
)

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
  )
```

Plot the datasets

```{r}
sim_df_const %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")

sim_df_nonconst %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r}
lm(y ~ x, data = sim_df_const) %>% broom::tidy()
lm(y ~ x, data = sim_df_nonconst) %>% broom::tidy()
```


The assumptions used to build the model are wrong. There is uncertainty in the estimates. How much? lets figure that out

We see the same amoung of uncertainty in the std.error in both estimates, but we know there is a difference, one is constant and the other is nonconstant. 

Our assumptions are not met, I need to understand what the distribution of my sampling should be using repeat sampling under bootstrap.

## Draw one bootstrap sample

```{r}
boot_samp = function(df) {
  sample_frac(df, replace = TRUE) %>% 
    arrange(x)
  
}
  #sample_frac(df, replace = TRUE). We are drawing sample with replacement from that df
```

Check if this works
```{r}
boot_samp(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm") + 
  ylim(-5, 16)
  
```
What we get: a df of 250, we get some info and some repeated info (because it has replacement)

```{r}
boot_samp(sim_df_nonconst) %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```

