---
title: "Cross Validation"
author: "Nidhi Patel"
date: "12/9/2020"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Simulate data
```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )
```

Look at data

```{r}
nonlin_df %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

## Cross Validation by hand

Get training and testing datasets
```{r}
train_df = sample_n(nonlin_df, size = 80)
test_df = anti_join(nonlin_df, train_df, by = "id") #anti_join takes the remaining data, according to the ID and makes the dataset with it
```

Fit three models

```{r}
lin_mod = lm(y ~ x, data = train_df)
smooth_mod = gam(y ~ s(x), data = train_df)
#gam is general additive model coming out of the mgcv package. saying y is a smooth fn of x
wiggly_mod = gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
# k tells us hoe specific we want that model to be. we are setting parameters (sp) to something VERY low to make it not smooth at all
```

Can I see what we just did

```{r}
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")
```

Wiggly chases too much. Smooth model does do best in terms of prediction accuracy. 

Can do multiple predictions at the same time:

```{r}
train_df %>% 
  gather_predictions(lin_mod, smooth_mod, wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") +
  facet_grid(. ~ model)
```

Look at prediction accuracy. Look at RMSE at testing data set.

```{r}
rmse(lin_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

Linear: very high, does not fit model at all. 
Wiggly: still high, not as bad.
Smooth: the best choice. Lowest RMSE.
