---
title: "Cross Validation"
author: "Nidhi Patel"
date: "12/9/2020"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Simulate data
```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )
```

Look at data

```{r}
nonlin_df %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

## Cross Validation by hand

Get training and testing datasets
```{r}
train_df = sample_n(nonlin_df, size = 80)
test_df = anti_join(nonlin_df, train_df, by = "id") #anti_join takes the remaining data, according to the ID and makes the dataset with it
```

Fit three models

```{r}
lin_mod = lm(y ~ x, data = train_df)
smooth_mod = gam(y ~ s(x), data = train_df)
#gam is general additive model coming out of the mgcv package. saying y is a smooth fn of x
wiggly_mod = gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
# k tells us hoe specific we want that model to be. we are setting parameters (sp) to something VERY low to make it not smooth at all
```

Can I see what we just did

```{r}
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")
```

Wiggly chases too much. Smooth model does do best in terms of prediction accuracy. 

Can do multiple predictions at the same time:

```{r}
train_df %>% 
  gather_predictions(lin_mod, smooth_mod, wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") +
  facet_grid(. ~ model)
```

Look at prediction accuracy. Look at RMSE at testing data set.

```{r}
rmse(lin_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

Linear: very high, does not fit model at all. 
Wiggly: still high, not as bad.
Smooth: the best choice. Lowest RMSE.

## Cross Validation using `modelr`

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) # we want 100 cross validations
```

What is happening here?
This makes a list of 100 cross validations. We can pull the test and training df from each and make it a tibble
```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as.tibble()
cv_df %>% pull(test) %>% .[[1]] %>% as.tibble()
```

We will convert all training and testing data sets and convert to tibble.
```{r}
cv_df = cv_df %>% 
mutate(train = map(train, as_tibble),
       test = map(test, as_tibble))
```

Let's try to fit models and get RMSEs for them

```{r}
cv_df = cv_df %>% 
  mutate(
    linear_mod = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_mod = map(.x = train, ~gam(y ~ s(x), data = .x)),
    wiggly_mod = map(.x = train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
# i not have lists containing model info for each of the cross validations. USE map2 for TWO vars going into the map
  mutate(
    rmse_linear = map2(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2(.x = smooth_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2(.x = wiggly_mod, .y = test, ~rmse(model = .x, data = .y))
  ) %>% 
   unnest(rmse_linear, rmse_smooth, rmse_wiggly)

  #pull(rmse_linear) # this is shows all the rsme for the linear models we are cross validating.

```

What doe these results dae about the model choices?

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```
Among the three models we're using, the smooth model is doing the best.

Comput averages:

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rmse = mean(rmse))
```


