---
title: "Linear Models"
author: "Nidhi Patel"
date: "12/8/2020"
output: github_document
---
```{r}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Import data

```{r}
data("nyc_airbnb")

airbnb = nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

## Fit a model
We want a line per each borough. 
```{r}
airbnb %>% 
  ggplot(aes(x = stars, y = price, color = boro)) +
  geom_point()
```

Let's fit the model we care about. relating price to starts and boro

```{r}
fit = lm(price ~ stars + boro, data = airbnb)
```

Look at the result

```{r, include = FALSE}
fit

summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
residuals(fit)
```

Let's look at the results better

```{r}
broom::glance(fit)
#this produces a tibble, rather than a matrix like the code chunk above

broom::tidy(fit) %>% 
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Boro: ")
  ) %>% 
  knitr::kable(digits = 3)

```

## Be in control of factors
In R, the default is for the first categorical variable, alphabetically, to be the reference class.  

Let's change that.  We will change the room type reference variable to be the most common within the "Room type" var.

```{r}
airbnb = airbnb %>% 
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type))

```

```{r}
airbnb %>% 
  ggplot(aes(x = stars, y = price, color = boro)) +
  geom_point()
```

We see that the model has not changed fundamentally, but reference has changed
```{r}
fit = lm(price ~ stars + boro, data = airbnb)
broom::tidy(fit)

broom::glance(fit)
```

