---
title: "Linear Models"
author: "Nidhi Patel"
date: "12/8/2020"
output: github_document
---
```{r}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Import data

```{r}
data("nyc_airbnb")

airbnb = nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

## Fit a model
We want a line per each borough. 
```{r}
airbnb %>% 
  ggplot(aes(x = stars, y = price, color = boro)) +
  geom_point()
```

Let's fit the model we care about. relating price to starts and boro

```{r}
fit = lm(price ~ stars + boro, data = airbnb)
```

Look at the result

```{r, include = FALSE}
fit

summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
residuals(fit)
```

Let's look at the results better

```{r}
broom::glance(fit)
#this produces a tibble, rather than a matrix like the code chunk above

broom::tidy(fit) %>% 
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Boro: ")
  ) %>% 
  knitr::kable(digits = 3)

```

## Be in control of factors
In R, the default is for the first categorical variable, alphabetically, to be the reference class.  

Let's change that.  We will change the room type reference variable to be the most common within the "Room type" var.

```{r}
airbnb = airbnb %>% 
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type))

```

```{r}
airbnb %>% 
  ggplot(aes(x = stars, y = price, color = boro)) +
  geom_point()
```

We see that the model has not changed fundamentally, but reference has changed
```{r}
fit = lm(price ~ stars + boro, data = airbnb)
broom::tidy(fit)

broom::glance(fit)
```

## Diagnostics

```{r}
airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = boro, y = resid)) + 
  geom_violin() +
  ylim(-500, 1500)


airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() + 
  facet_wrap(. ~ boro)
```

## Hypothesis tests

```{r}
fit %>% 
  broom::tidy()
```

What about significance of borough?

```{r}
fit_null = lm(price ~ stars, data = airbnb)
fit_alt = lm(price ~ stars + boro, data = airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

## Nest data, fit models

Whether there is an assoication between price and stars and weather it differs between boroughs.

This is pretty formal and also complex.

```{r}
fit = lm(price ~ stars * boro + room_type * boro, data = airbnb)

broom::tidy(fit)
```

This is more exploratory but maybe easier to understand

Fit models through each list!!!

In Manhattan, there is a sig association between stars and price. Pval of bronx is insignificant. We are not looking at interactions, so this is purely exploratory. 
```{r}
airbnb %>% 
  nest(data = -boro) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars, data = .x)),
    results = map(models, broom::tidy)
  ) %>% #.x is what i am iterating across
  #pull(results)
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(term == "stars")
```

Do the same, but for roomtype

```{r}
airbnb %>% 
  nest(data = -boro) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% #.x is what i am iterating across
  #pull(results)
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(term != "(Intercept)") %>% 
  select(boro, term, estimate) %>% 
  pivot_wider(
    names_from = boro,
    values_from = estimate
  )
```

Let's nest even more.....

fit linear models for every little neighborhood in manhattan
```{r}
airbnb %>% 
  filter(boro == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) +
  geom_point() +
  facet_wrap(.~term) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
```

